\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{letterpaper}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{booktabs}

\title{Character Sheet}
\author{Player Name}

\begin{document}

\maketitle

\section{Basic Information}
\begin{tabularx}{\linewidth}{lX}
\textbf{Name:} & Arryn \\
\textbf{Race:} & Human \\
\textbf{Class:} & Ranger \\
\textbf{Level:} & 1 \\
\textbf{Background:} & Arryn is a ranger from the forests of the kingdom of Arden, where she learned to track and hunt from an early age. She has a strong sense of duty to protect the innocent, and has dedicated her life to defending her homeland and its people from threats both external and internal. Arryn is skilled in stealth and survival, and is equally at home in the forests and the city. She is fiercely independent, but also deeply loyal to her friends and allies. \\
\textbf{Alignment:} & Neutral Good \\
\textbf{Experience Points:} & 0 \\
\end{tabularx}

\section{Ability Scores}
\begin{tabularx}{\linewidth}{lcccccc}
\toprule
& \textbf{STR} & \textbf{DEX} & \textbf{CON} & \textbf{INT} & \textbf{WIS} & \textbf{CHA} \\
\midrule
\textbf{Score} & 14 & 16 & 14 & 10 & 16 & 12 \\
\textbf{Modifier} & +2 & +3 & +2 & +0 & +3 & +1 \\
\bottomrule
\end{tabularx}

\section{Skills}
\begin{tabularx}{\linewidth}{lcc}
\toprule
& \textbf{Proficiency} & \textbf{Bonus} \\
\midrule
Acrobatics &  &  \\
Animal Handling &  &  \\
Arcana &  &  \\
Athletics &  &  \\
Deception &  &  \\
History &  &  \\
Insight &  &  \\
Intimidation &  &  \\
Investigation &  &  \\
Medicine &  &  \\
Nature &  &  \\
Perception &  & +5 \\
Performance &  &  \\
Persuasion &  &  \\
Religion &  &  \\
Sleight of Hand &  &  \\
Stealth &  & +5 \\
Survival &  & +5 \\
\bottomrule
\end{tabularx}

\section{Equipment}
\begin{itemize}[leftmargin=*]
\item Studded leather armor
\item Longbow and 20 arrows
\item Dagger
\item Bedroll
\item Backpack
\item 10 torches
\item 10 days of rations
\item Waterskin
\item 50 feet of hempen rope
\end{itemize}
\section{Features and Traits}
\begin{itemize}[leftmargin=*]
\item Favored Enemy: Arryn has advantage on Wisdom (Survival) checks to track and on Intelligence checks to recall information about her favored enemies (humanoids, beasts).
\item Natural Explorer: Arryn is proficient in the Survival skill and has advantage on initiative rolls while traveling for an hour or more.
\item Bonus Feat: Humans get an extra feat at level 1. Arryn has chosen the Archery feat, giving her a +2 bonus to attack rolls with ranged weapons.
\end{itemize}

\section{Spells}
\begin{tabularx}{\linewidth}{lcccc}
\toprule
\textbf{Level} & \textbf{Name} & \textbf{School} & \textbf{Casting Time} & \textbf{Range} \\
\midrule
 &  &  &  &  \\
 &  &  &  &  \\
 &  &  &  &  \\
 &  &  &  &  \\
 &  &  &  &  \\

\textbf{Duration} & \textbf{Components} & \textbf{Description} \\
\midrule
 &  &  &  &  &  &  \\
 &  &  &  &  &  &  \\
 &  &  &  &  &  &  \\
 &  &  &  &  &  &  \\
 &  &  &  &  &  &  \\
\bottomrule
\end{tabularx}

\section{Class Features}
\begin{itemize}[leftmargin=*]
\item 
\item 
\item 
\end{itemize}

\section{Hit Points}
\begin{tabularx}{\linewidth}{lcc}
\toprule
\textbf{Total Hit Points} & \textbf{Current Hit Points} & \textbf{Temporary Hit Points} \\
\midrule
10 & 10 & 0 \\
\bottomrule
\end{tabularx}

\section{Armor Class}
\begin{tabularx}{\linewidth}{lX}
\textbf{Armor Class:} & 16 (studded leather armor) \\
\textbf{Initiative:} & +3 \\
\textbf{Speed:} & 30 feet \\
\end{tabularx}

\section{Attacks and Spellcasting}
\begin{tabularx}{\linewidth}{lccX}
\toprule
\textbf{Name} & \textbf{Attack Bonus} & \textbf{Damage/Type} & \textbf{Properties} \\
\midrule
Longbow & +5 & 1d8+3 piercing & range 150/600 \\
Dagger & +5 & 1d4+3 piercing & 5 feet \\
\bottomrule
\end{tabularx}

\section{Personality Traits}
\begin{itemize}[leftmargin=*]
\item I'm always calm, no matter what the situation.
\item I'm always willing to listen to others.
\end{itemize}

\section{Ideals}
\begin{itemize}[leftmargin=*]
\item Duty: It is my duty to protect the innocent.
\end{itemize}

\section{Bonds}
\begin{itemize}[leftmargin=*]
\item I have sworn to protect the people of my homeland.
\end{itemize}

\section{Flaws}
\begin{itemize}[leftmargin=*]
\item I'm easily swayed by a good-looking face.
\end{itemize}

\end{document}
