\documentclass[12pt]{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1in]{geometry}
\usepackage{savetrees}

\author{Francesco Prem Solidoro}
\title{CV}

\titleformat{\subsection}
{}
{}
{0em}
{\large\bfseries}


\titleformat{\section}[frame]
{\Large}
{}
{.02em}
{\filcenter\bfseries}


\titleformat{\subsubsection}
{}
{}
{0em}
{\bfseries\underline}


\renewcommand{\maketitle}{
\begin{center}
{\huge\bfseries
\theauthor}
\end{center}
}

\begin{document}
\maketitle
\section{Personal Information}
\begin{itemize}
	\item \underline {Address:} Via S.Slataper, 39, 34079, Staranzano, Italy
	\item \underline {Phone:} +39 3272872455
	\item \underline{Email:} franci.solidoro@gmail.com
	\item \underline{Date of Birth:} 27/02/2003
\end{itemize}
\section{Profile}
I am an open minded and eclectic person. Curiosity is my drive, which leads me to investigate, dive deep, discover, and learn. I thrive on the new, the complex, and in the making of connections across
different subjects. I find great pleasure in completing complex tasks, and tend to seek them with excitement. As I have a strong interest in politics, I find the behaviour of people to be a really
interesting subject: how they interact with the systems they live within, how the culture they grew up in affects their world view, and where the foundations of their belief systems base themselves in.
\section{Education}
\subsection{2009 - 2014}
\subsubsection{State Elementary School ``Gianni Rodari , (Staranzano).}
\subsection{2014 - 2017}
\subsubsection{State First Degree Secondary School ``Dante Alighieri", (Staranzano).}
Musical curriulum: extra hours were spent on learning a musical instrument (flute) \\
Graduated with 10/10

\subsection{2017 - 2022}
\subsubsection{State High School ``I.S.I.S. Michelangelo Buonarroti", (Monfalcone).}
"liceo scientifico", Secondary school with focus on science, pysic and Mathematics
\begin{itemize}
	\item{Member of the Mathematics' olympiad school team}
	\item{52nd national in the Foreign Language (English) olympiad}
	\item{Participation to several extra curricular activities, such as public readings (Books in the city project), and theatre fruition} \\
Graduated with 100/100
\end{itemize}
\subsubsection{"Tartini" Conservatory of Music, (Trieste).}
\begin{itemize}
	\item{Study of flute and various complementary musical subjects: music theory, history, harmony, piano and chamber/ensemble music}
\end{itemize}
\subsection{2022-}
\subsubsection{UNIBO}
International course in Economics, Politics and Social Sciences (EPOS)
\subsubsection{Collegio Superiore di Bologna} % (fold)
Complementary to the UNIBO course, I was admitted in 3rd place.

\section{Other activities}
	\subsection{2012 -}
	Member of the city’s scout group “Staranzano 1”, Staranzano, Italy
Part of the AGESCI association, it's a group that follows the main principles of Baden Powell's scouts: cooperation, competence, self reflection, open mindedness, and integration with our social and natural surroundings.
    \subsection{2010 - 2020}
	    \begin{itemize}
			\item{Study of violin, played in a small orchestra, a violin trio, quartet and  various local scholastic enembles}
			\item{Played various sporst, with a focus on basketball and athletics}
		\end{itemize}
	\subsection{2017 - 2022}
	Member of the theatre group “La Barraca”, Staranzano, Italy
 	\begin{itemize}
		\item{Practice and multiple performances throught the year}
		\item{Plays from national and international authors, like Goldoni, Maurivaux, Beckett and Dickens.}
	\end{itemize}
\section{Skills}
	\subsection{Coputer Skills}
		\begin{itemize}
			\item{Basic knowledge of Python, c, clojure, Java and Posix}
			\item{Proficient in GNU/Linux, Windows and Mac OS}
			\item{Can use most office suites (g-suite, MS Office, LibreOffice, etc.)}
			\item{\LaTeX}
		\end{itemize}
	\subsection{Language Skills}
		\begin{itemize}
			\item{Italian: Native speaker}
			\item{English: C2}
			\item{French: Basic knowledge}
			\item{German: A1/A2}
		\end{itemize}
	\subsection{Other Skills}
	I've always had extremely solid soft skills: from oration to debate to normal conversation, I can comfortably craft arguments and play with words to suppoort my opinions.

\section{Additional information}
\underline{Interests and hobbies:}
I like to write, both poetry and prose, and compose music in my free
time. I also enjoy reading and have recently developed an interest in photography and programming.


\end{document}
